---
title: "R Markdown Presentation & Plotly"
author: "AGarcia"
date: "11/6/2018"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Peer-graded Assignment: R Markdown Presentation & Plotly

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!

## Dataset: oil-prices

Dataset used for the graphic is an anual oil-prices (brent) between May 1987 and September 2018. Data are taking monthly, from 15 of each month between the mentioned years.

Data was downloaded from this place:

https://github.com/datasets/oil-prices

## Brent: explanation 

A blended crude stream produced in the North Sea region which serves as a reference or "marker" for pricing a number of other crude streams

## Dataset preparation

Preprocesing the dataset was not needed on this case, just read the csv file.
An example of the dataset (head) is also displayed bellow.

```{r brent, echo = TRUE}
brent <- read.csv("brent-monthly.csv", header = TRUE)
head(brent)
```

## Slide with Plot

```{r load}
library(plotly)
```

```{r plot,  echo = TRUE}
plot_ly(brent, x = ~Date, y = ~Price, type = "scatter", mode = "lines")
```

